---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ForcePlate

<!-- badges: start -->
<!-- badges: end -->

The goal of the ForcePlate package is to extract and process features to characterize of a recorded stabilogram.

## Installation

You can install the development version of ForcePlate from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joergheintz/ForcePlate")
```

## Example: Derivatives of center point of force displacement

This is a basic example which shows you how to calculate a speed and acceleration. 
$$ 
\begin{aligned}
\dot{x_t} &= \frac{x_{t+1} - x_{t-1}}{2 \Delta t} \\
\ddot{x_t} &= \frac{x_{t+1} - 2 x_t + x_{t-1}}{2 \Delta t} \\
\end{aligned}
$$
```{r example}
library(ForcePlate)
library(ggplot2)
library(kableExtra)
library(tibble)


## basic example code
      time = seq(0.01,6.28, 0.01)
      distance = sin(time)
      df = derivatives(y = distance, t = time)
      
## output
      as_tibble(rbind(head(df, 3), tail(df, 3)))
      
```

The function "derivatives" takes time and response as vectors and returns data frame. The chosen algorithm requires 3 data points to estimate velocity and acceleration the data set is therefore reduced n - 2 records. The data frame output shows head and tail for the data set with the NA.   
  

```{r, fig.align = 'center', fig.height=4, fig.width=10}

# remove NA
      df = df[complete.cases(df), ]

# output
      ggplot(data = df) +  
      geom_point(aes(x = t, y = y ), color = 'brown', alpha = 0.5, size = 0.1) + 
      geom_point(aes(x = t, y = y.), color = 'darkgrey', alpha = 0.5, size = 0.1)  + 
      geom_point(aes(x = t, y = y.. ), color = 'darkgreen', alpha = 0.5, size = 0.1) +
            ylab(paste("y, y., y..")) + 
            xlab("time")
```
